Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2018-05-18 SupportingInformation.Rmd
log transforming the BMR, not just the mass

**bmr-contrasts.csv** : This contains the trait contrasts
from phylogenetically independent contrasts [@SukumaranH2010] 
of data reported by [@GenoudIM2017] on the basal metabolic rate (BMR)
and mass of mammals species.
Specifically, the "SELECT" BMR data in their database were used for
 those species for which data were available.
A phylogeny in NEXUS [@NEXUS] format was extracted from the 
 supplementary information of [@GenoudIM2017].
Version 4.4.0 of the DendroPy library [@SukumaranH2010] was used to calculate 
  phylogenetic independent contrasts using Python 2.7.
For each contrast, the path length spanned by the contrast (sum of the branch
  lengths) and the contrast for the mass, BMR and natural
  logarithm of the mass were written as a row in the bmr-contrasts.csv file.

>>>>

**bmr-contrasts.csv** : This contains the trait contrasts
from phylogenetically independent contrasts [@SukumaranH2010] 
of data reported by [@GenoudIM2017] on the basal metabolic rate (BMR)
and mass of mammals species.
Specifically, the "SELECT" BMR data in their database were used for
 those species for which data were available.
A phylogeny in NEXUS [@NEXUS] format was extracted from the 
 supplementary information of [@GenoudIM2017].
Version 4.4.0 of the DendroPy library [@SukumaranH2010] was used to calculate 
  phylogenetic independent contrasts using Python 2.7.
For each contrast, the path length spanned by the contrast (sum of the branch
  lengths) and the contrast for the mass, natural logarithm of the BMR and natural
  logarithm of the mass were written as a row in the bmr-contrasts.csv file.
